GVN-Hoist: Hoisting Computations from Branches

### 2016-08-05 hoist.tex
calls

\subsection{In the presence of calls}
Hoisting scalars across calls is tricky because it can increase the number of
spills. During the frame lowering of calls, the argument registers, in general,
the caller saved registers are saved because they might be modified by the
callee and after the call they are restored. So before the call the register
pressure is high because the number of available registers are reduced by the
number of caller saved registers. In that situation if a computation is hoisted
across the call, that would increase the total number of registers required by
one, thus contributing to the register pressure.

@@

>>>>

\subsection{In the presence of calls}
Hoisting scalars across calls is tricky because it can increase the number of
spills. During the frame lowering of calls, the argument registers, in general,
the caller saved registers are saved because they might be modified by the
callee and after the call they are restored \cite{frame-lowering}. So before the
call, the register pressure is high because the number of available registers
are reduced by the number of caller saved registers. In that situation if a
computation is hoisted across the call, that would increase the total number of
registers required by one, thus contributing to the register pressure.

@@

Hoisting memory references also require precise analysis of all the memory
addresses accessed by the call. In our implementation, since we only analyze the
callee declaration the analysis is very conservative. In the presence of pure
calls, loads can be hoisted but stores can't. Also, if the call throws exceptions,
or it it may not return, memory references cannot be hoisted.
